\speculake: Hiding Malware in Speculative Execution

### 2018-12-13 paper/abstract.tex
Minor fixes, added bandwidth recomputation to abstract and fixed cropping in figure 6
satisfying page constraints

We introduce \emph{\speculake}\footnote{Executable Spectre}, which compiles
arbitrary malicious code into a seemingly-benign payload binary. When a separate
trigger program runs on the same machine, it mistrains the CPU's branch
predictor, causing the payload program to \emph{speculatively} execute its malicious
payload, which communicates speculative results back to the rest of the payload program
to change its real-world behavior.

We study the extent and types of execution that can be performed
speculatively, and demonstrate several computations that can be
performed covertly. In particular, within speculative execution we are able to
decrypt memory using AES-NI instructions at over 5~kbps. Building on this, we
decrypt and interpret
a custom virtual machine language to perform arbitrary computation and system
calls in the real world. We demonstrate this with a proof-of-concept dial back shell,
which takes only a few milliseconds to execute after the trigger is issued.
We also show how our corresponding trigger program
can be a pre-existing benign application already running on the system, and
demonstrate this concept with OpenSSL driven remotely by the attacker as a
trigger program.

>>>>

We introduce \emph{\speculake}, which compiles
arbitrary malicious code into a seemingly-benign payload binary. When a separate
trigger program runs on the same machine, it mistrains the CPU's branch
predictor, causing the payload program to \emph{speculatively} execute its malicious
payload, which communicates speculative results back to the rest of the payload program
to change its real-world behavior.

We study the extent and types of execution that can be performed
speculatively, and demonstrate several computations that can be
performed covertly. In particular, within speculative execution we are able to
decrypt memory using AES-NI instructions at over 11~kbps. Building on this, we
decrypt and interpret
a custom virtual machine language to perform arbitrary computation and system
calls in the real world. We demonstrate this with a proof-of-concept dial back shell,
which takes only a few milliseconds to execute after the trigger is issued.
We also show how our corresponding trigger program
can be a pre-existing benign application already running on the system, and
demonstrate this concept with OpenSSL driven remotely by the attacker as a
trigger program.
